# Hex Stickers

```{r echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

Sys.Date()
```


```{r H1}
library(hexSticker) 
library(magick)
library(sysfonts)
library(tidyverse)


```

## La función y los valores "default"


```{r H2, eval=FALSE, message=FALSE}
sticker(
  subplot,
  s_x = 0.8,
  s_y = 0.75,
  s_width = 0.4,
  s_height = 0.5,
  package,
  p_x = 1,
  p_y = 1.4,
  p_color = "#FFFFFF",
  p_family = "Aller_Rg",
  p_fontface = "plain",
  p_size = 8,
  h_size = 1.2,
  h_fill = "#1881C2",
  h_color = "#87B13F",
  spotlight = FALSE,
  l_x = 1,
  l_y = 0.5,
  l_width = 3,
  l_height = 3,
  l_alpha = 0.4,
  url = "",
  u_x = 1,
  u_y = 0.08,
  u_color = "black",
  u_family = "Aller_Rg",
  u_size = 1.5,
  u_angle = 30,
  white_around_sticker = FALSE,
  ...,
  filename = paste0(package, ".png"),
  asp = 1,
  dpi = 300
)
```

***


**Arguments**

```{r, H3, echo=FALSE}
argumentos=tribble(
  ~Función, ~Descripción,
  "subplot"	, "subplot",

 "s_x",  "x position for subplot",
  "s_y",	"y position for subplot",

"s_width","width for subplot",
  

"s_height","height for subplot",

"package",	 "package name",

"p_x",	 "x position for package name",

"p_y",	 "y position for package name",

"p_color",	 "color for package name",

"p_family",	 "font family for package name",

"p_fontface",	 "fontface for package name",

"p_size",	 "font size for package name",

"h_size",	 "size for hexagon border",

"h_fill",	"color to fill hexagon",

"h_color",	 "color for hexagon border",

"spotlight",	 "whether add spotlight",

"l_x",	 "x position for spotlight",

"l_y", "y position for spotlight",

"l_width",	 "width for spotlight",

"l_height",	 "height for spotlight",

"l_alpha",	 "maximum alpha for spotlight",

"url",	"url at lower border",

"u_x",	"x position for url",

"u_y",	 "y position for url",

"u_color",	"color for url",

"u_family",	"font family for url",

"u_size",	"text size for url",

"u_angle",	"angle for url",

"white_around_sticker",	"default to FALSE. If set to TRUE, it puts white triangles in the corners",

"..."	, "additional parameter to geom_pkgname",

"filename",	 "filename to save sticker",

"asp",	 "aspect ratio, only works if subplot is an image file",

"dpi",	 "plot resolution",
)
```


```{r H4}
library(gt)
gt(argumentos)
```

Other Details,
 - The extension given in filename determines the graphics device that is used to render the sticker, e.g. filename = 'sticker.png' creates a png file and filename = 'sticker.svg' creates a svg file. For a list of supported graphics devices please see the documentation of ggplot2::ggsave()




sysfonts::font_add_google("Sixtyfour Convergence")
sysfonts::font_add_google("Rubik")
sysfonts::font_add_google("Young Serif") ## No baja

## Ejemplo de Crear un Hex con un gatito

```{r H5}

font_files()  #a list of all fonts available

## Loading Google fonts (https://fonts.google.com/)

sysfonts::font_add_google("Dancing Script") # selección de fonts de google
sysfonts::font_add_google("Bebas Neue")
sysfonts::font_add_google("Fuggles")
sysfonts::font_add_google("Roboto")
sysfonts::font_add_google("Lobster")
sysfonts::font_add_google("Raleway")


cat_img=image_read('cat.jpg')
analitica_img=image_read('Analitica3.png')

sticker(
  subplot= analitica_img,
  package="Meow",
  s_width =.75,
  s_height = .75,
  s_x=1,
  s_y=.75,
  p_size=19,
  p_x = 1.0,
  p_y = 1.5,
  p_color= 'purple',
  p_family= "Raleway",
  h_fill ='gold',
  h_color='hotpink',
  h_size = 2,
  url="www.cat.foundation.com",
  u_size=4,
  u_color = "violetred",
  spotlight=T

) %>% print

```

